---
title: "Ip.rmd"
output: html_document
---
## as an lp problem without taking x1 and x2 as integers
```{r}
library("lpSolveAPI")
x <- read.lp("ip.lp")
x
```

```{r}
solve(x)
get.objective(x)

```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## we are solving the x1 branch,integer programming with x1<=3
```{r}
library("lpSolveAPI")
x <- read.lp("ip1.lp")
x
```

```{r}
solve(x)
get.objective(x)
```
```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1>=4

```{r}
x <- read.lp("ip2.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)

```

```{r}
get.variables(x)
```

## integer programming with x2<=1

```{r}
x <- read.lp("ip3.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x2>=2

```{r}
x <- read.lp("ip4.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1=4

```{r}
x <- read.lp("ip5.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1>=5

```{r}
x <- read.lp("ip6.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```
## we are solving the x2 branch, integer programming with x2<=2

```{r}
x <- read.lp("ip7.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x2>=3

```{r}
x <- read.lp("ip8.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1<=3

```{r}
x <- read.lp("ip9.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1>=4

```{r}
x <- read.lp("ip10.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x2<=1

```{r}
x <- read.lp("ip3.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x2>=2

```{r}
x <- read.lp("ip4.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1=4

```{r}
x <- read.lp("ip5.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## integer programming with x1>=5

```{r}
x <- read.lp("ip6.lp")
x
```

```{r}
solve(x)
get.objective(x)
```

```{r}
get.constraints(x)
```

```{r}
get.variables(x)
```

## our optimal solution is x1=5 and x2=0, objective function= 40